Can we use masked priming in an online setting?

### 2021-05-27 MaskedPriming_complete_mspg.Rmd
update OSF link in manuscript

The study was pre-registered on the Open Science Framework (OSF) prior to data collection. The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/d2txs/.

@@

@@

load("blmm_exp1_rt_dist_full_ranef_5000.RData")
# This file does not fit on GitHub
# Download it at https://1drv.ms/u/s!ApE7JQmoH0baocARuxg21SFrS4riyg?e=8ZgbHA
# model name is blmm_exp1_rt_dist

@@

# This file does not fit on GitHub
# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobQPat43HR3ixhuqww?e=VySttd
# Relatedness = Condition

>>>>

The study was pre-registered on the Open Science Framework (OSF) prior to data collection. The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/57rzq/.

@@

The study was pre-registered on OSF. The pre-registration form, stimuli used in the experiment, scripts to run the experiment, data files, and data analyses are presented in the following OSF link: https://osf.io/fdtv5/

@@

load("blmm_exp1_rt_dist_full_ranef_5000.RData")
# 
# model name is blmm_exp1_rt_dist

@@

# Relatedness = Condition
